Concurrent semantics for left-linear rewriting [in adhesive categories]

### 2024-09-09 domains/domains.tex
section domains

CONCUR ruslts: strong enforcing + well-switching => nice behaviour of independence.

@@

   implies

@@

   - well-behaved with respect to quotients, e.g.,
   \begin{enumerate}
   \item  if we can rewrite G with L <- K -> R and we take a quotient
     of G which factories through the colimit, then we can still rewrite

   \item if we can rewrite G with L <- K -> R and we take a G' which
     has G as a quotient and we can find a match in G' (which factorises
     through the quotient) then we can still rewrite

   \item existence of the "largest" quotient to which a rule applies

   \item independence "in the colimit" [notes pag. 20-22 for ordinary
     derivations, then adapt to derivations up to fusion, which are ordinary
     derivations in the quotient]
   \end{enumerate}

@@

\subsubsection*{3.1 Domain of traces}
finitary, coherent, irreducible algebraic
    characterise irreducibles [traces with last step not switchable]
    [notes page 1-9, holds in general in the setting of concur]

@@

    - Interchargeability relation and its characterisation via the notion
    of derivation up to fusion

    - derivations up to fusion and properties [notes pag. 24-27]

    - characterising the interchangeability relation using
    derivations up to fusion [some idea at pag. 29, notes]

    - proving the interchangeability axioms to conclude that we
    obtain a weak prime domain [pag. 30-32, notes]

>>>>

CONCUR results: strong enforcing + well-switching => nice behaviour of independence.

@@

$\Rightarrow$

@@

- well-behaved with respect to quotients, e.g.,

\begin{enumerate}[a.]
\item  if we can rewrite $G$ with $L \leftarrow K \to R$ and we take a quotient
  of $G$ which factorises through the colimit, then we can still rewrite

\item if we can rewrite $G$ with $L \leftarrow K \to R$ and we take a $G'$ which
  has $G$ as a quotient and we can find a match in $G'$ (which factorises
  through the quotient) then we can still rewrite

\item existence of the ``largest'' quotient to which a rule applies

\item independence ``in the colimit'' [notes pag. 20-22 for ordinary
  derivations, later adapt to derivations up to fusion, which are ordinary
  derivations in the quotient]
\end{enumerate}

@@

\subsubsection*{3.1 Domain of traces}

\begin{enumerate}[a.]

\item  finitary, coherent, irreducible algebraic

\item need of characterising the  irreducibles: traces with last step not switchable
\end{enumerate}

[notes page 1-9, this holds in general in the setting of concur]

@@

\begin{enumerate}[a.]

\item Interchargeability relation and its characterisation via the notion
  of derivation up to fusion

\item derivations up to fusion and properties [notes pag. 24-27]

\item characterising the interchangeability relation using
derivations up to fusion [some idea at pag. 29, notes]

\item  proving the interchangeability axioms to conclude that we
obtain a weak prime domain [pag. 30-32, notes]
\end{enumerate}
